The dynamics of starvation and recovery

### 2017-03-21 Manuscript/Revision_2017/18.tex
minor edits to figs and orientation

\bibitem{CalderIII:1983jd}
Calder~III WA
\newblock (1983) {An allometric approach to population cycles of mammals}.
\newblock \emph{J. Theor. Biol.} 100:275--282.

\bibitem{Peterson:1984hj}
Peterson RO, Page RE, Dodge KM
\newblock (1984) {Wolves, moose, and the allometry of population cycles}.
\newblock \emph{Science} 224:1350--1352.

\bibitem{Krukonis:1991fk}
Krukonis G, Schaffer WM
\newblock (1991) {Population cycles in mammals and birds: Does periodicity
  scale with body size?}
\newblock \emph{J. Theor. Biol.} 148:469--493.

\bibitem{Hendriks:2012fc}
Hendriks AJ, Mulder C
\newblock (2012) {Delayed logistic and Rosenzweig{\textendash}MacArthur models
  with allometric parameter setting estimate population cycles at lower trophic
  levels well}.
\newblock \emph{Ecol Complex} 9:43--54.

\bibitem{Kendall:1999iy}
Kendall BE, {et~al.}
\newblock (1999) {Why do populations cycle? A synthesis of statistical and
  mechanistic modeling approaches}.
\newblock \emph{Ecology} 80:1789--1805.

\bibitem{Hogstedt:2005cr}
H{\"o}gstedt G, Seldal T, Breistol A
\newblock (2005) {Period length in cyclic animal populations}.
\newblock \emph{Ecology} 86:373--378.

\bibitem{Kendall:1998hl}
Kendall, Prendergast, Bjornstad
\newblock (1998) {The macroecology of population dynamics: taxonomic and
  biogeographic patterns in population cycles}.
\newblock \emph{Ecol. Lett.} 1:160--164.

@@

\end{thebibliography}
}

>>>>

@@

\end{thebibliography}

}
